How has the Brazilian Amazon been constructed as a problem:Presidential speeches and transnational politics since 1985

### 2022-09-21 Draft_September_2022/Full_draft_20220901.rmd
#textwithconfidenceintervalsandprobabilities

```{=latex}
\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, deforestation}
```
```{=latex}
\wordcount{ 8470 (including abstract, text, references, and and footnotes)}
```
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(readxl)
library(ggplot2)
library(gridExtra)
library(sjPlot)
library(parameters)

@@

We convert log odds from Table 1, below, into probabilities [^2]. It shows that for each 1000Km increase, we find an increase of 52.8% in the predicted probability of constructing the Amazon as an issue of environmental preservation. That is, the farthest away the president is from the Amazon region, the more likely the president is to construct it as an issue of environmental conservation. Second,the opposite is true for both economic integration (and social development): for an increase of 1000Km, we find a decrease of 48.5% (47.4%), respectively. When speaking within the Amazon, presidents focus on social development and economic integration. This entails that conservation might be a desirable construction when speaking internationally about the Amazon, but not at the local level, where presidents highlight economic and social development. This multi-level game implies that presidents talk to the economic and social needs of the people domestically while boasting about environmentalism internationally. Finally, national sovereignty problem constructions do not appear to change with distance.

@@

@@

```{r Table 3, fig.cap="Odds Ratio and Confidence Intervals", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

>>>>

```{=latex}
\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, deforestation}
```

```{=latex}
\wordcount{ 8470 (including abstract, text, references, and and footnotes)}
```

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(readxl)
library(ggplot2)
library(gridExtra)
library(sjPlot)
library(parameters)

@@

We convert log odds from Table 1, below, into probabilities and report the 95% confidence interval in the subsequent sentences [^2]. First, we find that for each 1000Km increase in distance, there is an increase between 51.92% and 53.91% in the predicted probability of constructing the Amazon as an issue of environmental preservation. That is, the farthest away presidents are from the Amazon region, the more likely they are to construct it as an issue of environmental conservation. Second,the opposite is true for economic integration (and social development): for an increase of 1000Km in distance, we find a decrease between 47.36% (45.35%) and 49.74% (49.23%), respectively. When speaking within the Amazon, presidents focus on social development and economic integration. This entails that conservation might be a desirable construction when speaking internationally about the Amazon, but not at the local level, where presidents highlight economic and social development. This multi-level game implies that presidents talk to the economic and social needs of the people domestically while boasting about environmentalism internationally. Finally, national sovereignty problem constructions do not appear to change with distance.

@@

odd2prob <- function(x){
  prob <- x / (1 + x)
  return(prob)
}
```

@@

```{r Table 3, eval=FALSE, fig.cap="Odds Ratio and Confidence Intervals", message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE, results="asis"}
